\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-02-25 tex/paper.tex
Added references

\subsubsection{Conflict Resolution}
If the persistent storage would be distributed the different database nodes would have to have rules
set up for conflict resolution as this model does not consider what to do if the same meta data is
modified on the nodes before they have time to synchronise. The easiest way to handle this is to
have the clocks on the nodes synchronised and timestamp each change and when synchronising the nodes
only consider the newest data if there is a conflict. This will have the same result as concurrent
modification with a single database node with this model, namely last write
wins~\cite{LASTWRITEWINS}.

@@

\subsubsection{Perius}
As the persistent storage, used in this implementation (Section~\ref{sec:persistent_storage}), does
not implement transactions or locks a lot of different problems can occur when several clients are
working on the same data set at the same time. Such problems could be race conditions or determining
the happened-before relation. In this work this problem is solved by implementing Copy-on-Write on
data with high consistency requirements.

@@

\fix Relate section more to comparison

>>>>

\subsubsection{Conflict Resolution} \label{sec:conflict_res}
If the persistent storage would be distributed the different database nodes would have to have rules
set up for conflict resolution as this model does not consider what to do if the same meta data is
modified on the nodes before they have time to synchronise. The easiest way to handle this is to
have the clocks on the nodes synchronised and timestamp each change and when synchronising the nodes
only consider the newest data if there is a conflict. This will have the same result as concurrent
modification with a single database node with this model, namely last write
wins~\cite{LASTWRITEWINS}.

@@

\subsubsection{Perius}
As the persistent storage, used in this implementation (Section~\ref{sec:persistent_storage}), does
not implement transactions or locks a lot of different problems can occur when several clients are
working on the same data set at the same time. Such problems could be race conditions or determining
the happened-before relation~\cite{LAMPORT}. In this work the race condition problem is solved by 
implementing Copy-on-Write on data with high consistency requirements. The happened-before relation
is not fully solved, but suggestions of how to solve it is given in Section~\ref{sec:conflict_res}.

@@
